---
title: "esm206_lab6 - Linear Regression"
author: "Sage Davis"
date: "11/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## RAnk based test example

Mann-_Whitney U (non-parametric alternative to an unpaired 2-sample t-test)

H0: Equal ranks (or medians)
HA: Ranks not equal (medians)

### Create some samples 

'set.seed()'  to create "psuedorandom but reproducible samples"

If we all have same starting point then we all have the same reference...

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)  # replace allow for doubles
gp_1

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)  # replace = TRUE allow for doubles
gp_2
```
Take a look at the distribution using 'hist()'

```{r}
hist(gp_1)
hist(gp_2)
```

Try a t-test to compare results

```{r}
ttest <- t.test(gp_1, gp_2)

ttest
# if these are paired you can add
# probability of 19.8% that two samples with means that are at least differrent this by

```

This p-value means if our samples are drawn from populations with the same mean (i.e., if the null hyp is true), there is a `r round(ttest$p.value,2)` prob of finding samples means "at lease as different" as mine by random chance.  

[A more comprehensive explanation of diff between groups  ... actually means, data spreads, effect size  ..there is not significant difference (t(dF0)) = t-statistical value, p = )]

### Mann Whitney U rank based test

We will use the 'wilcox.test()' fuct to perform a 2 sample rank-based test

```{r}
mwu <- wilcox.test(gp_1, gp_2)

mwu
```

This p-value means that if our samples are drawn from populations with the same median (i.e., if the null hyp is true), there is a `r round(mwu$p.value,2)` prob  of finding samples means "at lease as different" as mine by random chance. 

Concl:  No sign diff between medians (Mann_Whitney U; U = `r mwu$statistic, p = round(mwu$p.value, 3)`)

The median of group A (M= 22.4g) and group B

